---
title: "20201025-p8133_computingscratch_jsg2145"
author: "Jared Garfinkel"
date: "10/25/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
output1 = vector(mode = "list", length = 20)
for(i in 1:20) {
  output1[[i]] = bind_cols("n1_response" = i)
  output1[[i]]$x = list(seq(from = 0.01, to = 0.4, by = 0.003))
}

output1 = bind_rows(output1) %>% 
  unnest(x) %>% 
  nest(x)

goutput1 = output1 %>% 
  filter(n1_response > 5)
```


```{r}
output2 = vector(mode = "list", length = 400)
for (i in 1:20) {
  for (j in 1:20) {
    output2[[c(i, j)]] = bind_cols("n1_response" = i, "n2_response" = j)
    output2[[c(i, j)]]$x = list(seq(from = 0.01, to = 0.4, by = 0.003))
  }
  output2[[i]] = map(output2[[i]], ~bind_rows(.))
}


output2 = bind_rows(output2) %>% 
  unnest(x) %>% 
  nest(x)

goutput2 = output2 %>% 
  filter(n1_response > 5,
         (n1_response + n2_response) > 11)
```


```{r}
output3 = vector(mode = "list", length = 8000)
for (i in 1:20) {
  for (j in 1:20) {
    output3[[c(i, j)]] = bind_cols("n1_response" = i, "n2_response" = j)
    output3[[c(i, j)]]$k = list(seq(from = 1, to = 20))
    output3[[c(i, j)]]$x = list(seq(from = .01, to = 0.4, by = 0.003))
  }
  output3[[i]] = map(output3[[i]], ~bind_rows(.))
}

output3 = bind_rows(output3) %>% 
  rename("n3_response" = k) %>% 
  unnest(n3_response) %>% 
  unnest(x) %>% 
  nest(x)

goutput3 = output3 %>% 
  filter(n1_response > 5,
         (n1_response + n2_response) > 11,
         (n1_response + n2_response + n3_response) > 17)
```


```{r}
output4 = vector(mode = "list", length = 88000)
for (i in 1:20) {
  for(j in 1:20) {
    output4[[c(i, j)]] = bind_cols("n1_response" = i, "n2_response" = j)
    output4[[c(i, j)]]$k = list(seq(from = 1, to = 20))
    output4[[c(i, j)]]$l = list(seq(from = 1, to = 11))
    output4[[c(i, j)]]$x = list(seq(from = .1, to = 0.16, by = 0.003))
    output4[[c(i, j)]]$n1 = 6
    output4[[c(i, j)]]$n2 = list(seq(12, 14))
    output4[[c(i, j)]]$n3 = list(seq(18, 20))
    output4[[c(i, j)]]$n4 = 24
  }
  output4[[i]] = map(output4[[i]], ~bind_rows(.))
}

output4 = bind_rows(output4) %>% 
  rename("n3_response" = k,
         "n4_response" = l) %>%
  unnest(n3_response) %>% 
  unnest(n4_response) %>% 
  unnest(n1) %>% 
  unnest(n2) %>% 
  unnest(n3) %>% 
  unnest(n4) %>% 
  unnest(x)

goutput4 = output4 %>%
  filter(n1_response > n1-1,
         (n1_response + n2_response) > n2-1,
         (n1_response + n2_response + n3_response) > n3-1,
         (n1_response + n2_response + n3_response + n4_response) > n4-1) %>% 
  nest(x)

nrow(goutput4)
```


```{r, echo = FALSE, eval = FALSE}
# goutput2 = vector(mode = "list", length = 4)
# goutput2[[1]] = output2 %>% 
#   select(n1_response) %>% 
#   filter(n1_response > 5) %>% 
#   distinct()
# goutput2[[2]] = output2 %>% 
#   select(n1_response, n2_response) %>% 
#   filter(n1_response > 5,
#          (n1_response + n2_response) > 11) %>% 
#   distinct()
# goutput2[[3]] = output2 %>% 
#   select(n1_response, n2_response, n3_response) %>% 
#   filter(n1_response > 5,
#          (n1_response + n2_response) > 11,
#          (n1_response + n2_response + n3_response) > 17) %>% 
#   distinct()
# goutput2[[4]] = output2 %>% 
#   select(n1_response, n2_response, n3_response, n4_response) %>% 
#   filter(n1_response > 5,
#          (n1_response + n2_response) > 11,
#          (n1_response + n2_response + n3_response) > 17,
#          (n1_response + n2_response + n3_response + n4_response) > 23) %>% 
#   distinct()
  # goutput2[[i]] = output2 
  #   filter(output[[i]] > 5)
  # goutput2[[i+1]]
  #          (n1_response + n2_response) > 11,
  #          (n1_response + n2_response + n3_response) > 17,
  #          (n1_response + n2_response + n3_response + n4_response) > 23)

```

```{r}
prior1 = function(df = output1, null = 0.25, stage1n = 20, n1 = 6) {
  res = df %>% 
    unnest(data) %>% 
    mutate(pE1 = dbeta(null, n1_response/stage1n, (stage1n-n1_response)/stage1n),
           pS = dbeta(null+x, 25, 75)) %>% 
    filter(n1_response > n1-1)
  res1 = res %>%
    filter(pE1 > pS) %>%
    group_by(x) %>%
    mutate(alpha = 1 - length(x)/nrow(goutput1)) %>%
    select(x, alpha) %>%
    distinct() %>%
    filter(alpha < .2)
  return(res1)
}
```


```{r}
prior2 = function(df = output2, null = 0.25, stage1n = 20, stage2n = 40, n1 = 6, n2 = 12) {
  res = df %>% 
    unnest(data) %>% 
    mutate(pE1 = dbeta(null, n1_response/stage1n, (stage1n-n1_response)/stage1n),
           pE2 = dbeta(null, (n1_response+n2_response)/stage2n, (stage2n-n1_response-n2_response)/stage2n),
           pS = dbeta(null+x, 25, 75)) %>% 
    filter(n1_response > n1-1,
           (n1_response + n2_response) > n2-1)
  res2 = res %>%
    filter(pE2 > pS) %>%
    group_by(x) %>%
    mutate(alpha = 1 - length(x)/nrow(goutput2)) %>%
    select(x, alpha) %>%
    distinct() %>%
    filter(alpha < .2)
  return(res2)
}
```


```{r}
prior3 = function(df = output3, null = 0.25, stage1n = 20, stage2n = 40, stage3n = 60, n1 = 6, n2 = 12, n3 = 18) {
  res = df %>% 
    unnest(data) %>% 
    mutate(pE1 = dbeta(null, n1_response/stage1n, (stage1n-n1_response)/stage1n),
           pE2 = dbeta(null, (n1_response+n2_response)/stage2n, (stage2n-n1_response-n2_response)/stage2n),
           pE3 = dbeta(null, (n1_response + n2_response + n3_response)/stage3n, (stage3n-n1_response-n2_response-n3_response)/stage3n),
           pS = dbeta(null+x, 25, 75)) %>% 
    filter(n1_response > n1-1,
           (n1_response + n2_response) > n2-1,
           (n1_response + n2_response + n3_response) > n3-1)
  res3 = res %>%
    filter(pE3 > pS) %>%
    group_by(x) %>%
    mutate(alpha = 1 - length(x)/nrow(goutput3)) %>%
    select(x, alpha) %>%
    distinct() %>%
    filter(alpha < .2)
  return(res3)
}
```


```{r, cache = TRUE}
prior4 = function(df = output4, null = 0.25, stage1n = 20, stage2n = 40, stage3n = 60, stage4n = 71) {
  # res = vector(mode = "list", length = 9)
  # for (i in 1:3) {
  #   for (j in 1:3) {
  res4 = df %>% 
    mutate(pE1 = dbeta(null, n1_response/stage1n, (stage1n-n1_response)/stage1n),
           pE2 = dbeta(null, (n1_response+n2_response)/stage2n, (stage2n-n1_response-n2_response)/stage2n),
           pE3 = dbeta(null, (n1_response + n2_response + n3_response)/stage3n, (stage3n-n1_response-n2_response-n3_response)/stage3n),
           pE4 = dbeta(null, (n1_response + n2_response + n3_response + n4_response)/stage4n, (stage4n-n1_response-n2_response-n3_response-n4_response)/stage4n),
           pS = dbeta(null+x, 25, 75)) %>% 
    filter(pE1 > pS,
           pE2 > pS,
           pE3 > pS,
           pE4 > pS)
  
  response1 = res4 %>% 
    group_by(n1_response) %>% 
    summarize(nresponse = n(),
              n1 = n1,
              x = x) %>% 
    distinct()
  
  response2 = res4 %>% 
    group_by(n2_response) %>% 
    summarize(nresponse = n(),
              n1 = n1,
              n2 = n2,
              x = x) %>% 
    distinct()
  response3 = res4 %>% 
    group_by(n3_response) %>% 
    summarize(nresponse = n(),
              n1 = n1,
              n2 = n2,
              n3 = n3,
              x = x) %>% 
    distinct()
  response4 = res4 %>% 
    group_by(n4_response) %>% 
    summarize(nresponse = n(),
              n1 = n1,
              n2 = n2,
              n3 = n3,
              n4 = n4,
              x = x) %>% 
    distinct()
  # responses = cbind(response1, response2, response3, response4)
#   return(responses)
# }
    # group_by(x) %>% 
    # mutate(nx = nrow(.)) 
    # summarize(n1_response = n1_response,
    #           n2_response = n2_response,
    #           n3_response = n3_response,
    #           n4_response = n4_response,
    #           nx = nx,
    #           x = x, 
    #           n1 = n1,
    #           n2 = n2,
    #           n3 = n3,
    #           n4 = n4)
  paired_up1 = res4 %>% 
    filter(n1_response > n1-1) %>% 
    summarize(sum_n1 = n(),
              n1 = n1,
              x = x) %>% 
    distinct()
  paired_up2 = res4 %>% 
    filter((n1_response + n2_response) > n2-1) %>% 
    summarize(sum_n2 = n(),
              n1 = n1,
              n2 = n2,
              x = x) %>% 
    distinct()
  paired_up3 = res4 %>% 
    filter((n1_response + n2_response + n3_response) > n3-1) %>% 
    summarize(sum_n3 = n(),
              n1 = n1,
              n2 = n2,
              n3 = n3,
              x = x) %>% 
    distinct()
  paired_up4 = res4 %>% 
    filter((n1_response + n2_response + n3_response + n4_response) > n4-1) %>% 
    summarize(sum_n4 = n(),
              n1 = n1,
              n2 = n2,
              n3 = n3,
              n4 = n4,
              x = x) %>% 
    distinct()
  
  alpha_df1 = left_join(response1, paired_up1, by = c("n1", "x"), copy = TRUE)
  alpha_df2 = left_join(response2, paired_up2, by = c("n1", "n2", "x"), copy = TRUE)
  alpha_df3 = left_join(response3, paired_up3, by = c("n1", "n2", "n3", "x"), copy = TRUE)
  alpha_df4 = left_join(response4, paired_up4, by = c("n1", "n2", "n3", "n4", "x"), copy = TRUE)
  
  alpha_df = c(alpha_df1, alpha_df2, alpha_df3, alpha_df4)
  return(alpha_df)
}

prior4 = prior4()

str(prior4)
data.frame(prior4[6:11]) %>% 
  tibble() %>% 
  group_by(n1, n2, x) %>% 
  summarize(alpha = 1 - sum(nresponse)/sum_n2,
            x = x) %>% 
  filter(alpha < 0.2)
data.frame(prior4[1:5])
data.frame(prior4[12:18]) %>% 
  tibble() %>% 
  group_by(x) %>% 
  summarize(alpha = 1 - nresponse/sum_n3,
            x = x) %>% 
  filter(alpha < 0.2)

data.frame(prior4[19:26])
```


```{r, cache = TRUE}
# alpha1 = 1 - pull(response1, nresponse1)/pull(paired_up1, sum_n1)
  # alpha2 = 1 - pull(response2, nresponse2)/pull(paired_up2, sum_n2)
  # alpha3 = 1 - pull(response3, nresponse3)/pull(paired_up3, sum_n3)
  # alpha4 = 1 - pull(response4, nresponse4)/pull(paired_up4, sum_n4)
  # 
  # alphas = cbind(alpha1, alpha2, alpha3, alpha4)
  
  # for (i in 1:4) {
  #   outcomes[[i]] = responses[[i]] %>% 
  #     list(x = list(x),
  #            alpha1 = list(1 - nresponse/pull(paired_up1, sum_n1), n1),
  #            alpha2 = list(1 - nresponse/pull(paired_up2, sum_n2), n1, n2),
  #            alpha3 = list(1 - nresponse/pull(paired_up3, sum_n3), n1, n2, n3),
  #            alpha4 = list(1 - nresponse/pull(paired_up4, sum_n4), n1, n2, n3))
  # }
  return(outcomes)
}
  #   res[[i]] = map(res[[i]], ~bind_rows(.))
  # }
# }

#       res4 = res %>%
#         filter(pE4 > pS,
#                pE3 > pS,
#                pE2 > pS,
#                pE1 > pS)
#   return(res4)
# }
```

```{r}
prior1 = prior1()
prior2 = prior2()
prior3 = prior3()
prior4 = prior4()

prior4[[1]]

prior1
prior2
prior3
prior4 %>% 
  group_by(x) %>% 
  mutate(nx = n()) %>% 
  summarize(x = x,
            nx = nx,
            n1 = n1,
            n2 = n2,
            n3 = n3,
            n4 = n4,
            n1_response = n1_response,
            n2_response = n2_response,
            n3_response = n3_response,
            n4_response = n4_response,
            alpha = 1 - nx/nrow(goutput4)) %>% 
  filter(alpha < 0.2) %>% 
  select(x, alpha, everything()) %>% 
  arrange(x, alpha) %>% 
  distinct()
  # distinct() %>% 
  # arrange(x, alpha)

left_join(prior1, prior2, by = "x") %>% 
  left_join(prior3, by = "x") %>% 
  left_join(prior4, by = "x")
```

```{r}
#delta = 0.134, alpha = 0.164
set.seed(1)
n_sim = 10e5
x = seq(0.1, 0.199, by = .003)
dat = tibble(sums = c(sum(rbeta(n_sim, shape1 = 6.5, shape2 = 15.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 5.5, shape2 = 16.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 12.5, shape2 = 29.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 11.5, shape2 = 30.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 18.5, shape2 = 43.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 17.5, shape2 = 44.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 24.5, shape2 = 48.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 23.5, shape2 = 49.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim))
dat
```


When pE = 0.4,

```{r}
prior1 = prior1(null = 0.4)
prior2 = prior2(null = 0.4)
prior3 = prior3(null = 0.4)
prior4 = prior4(null = 0.4)

prior1
prior2
prior3
prior4
```

```{r}
adap = function(df = "output1") {
  m = str_trunc(df, 1, side = "left", ellipsis = "")
  var = paste0("n", m, "_response")
  output1 = vector(mode = "list", length = 20)
  for(i in 1:20) {
    df[[i]] = bind_cols(var = i)
    df[[i]]$x = list(seq(from = 0.01, to = 0.4, by = 0.003))
  }
  
  df = bind_rows(df) %>% 
    unnest(x) %>% 
    nest(x)
  return(df)
}
output1 = adap()
```

```{r}
str_trunc("output1", 1, side = "left", ellipsis = "")[1]
```


```{r}
output2 = output1 %>% 
  mutate(data2 = map(data, ~adap(df = "output2")))

output2
```




```{r}
output = vector(mode = "list", length = 20)
for (i in 1:20) {
  for (j in 1:51) {
    output[[c(i, j)]] = bind_cols("n1_response" = i, "n2_response" = j)
    output[[c(i, j)]]$x = list(seq(from = 0.01, to = 0.4, by = 0.003))
  }
  output[[i]] = map(output[[i]], ~bind_rows(.))
}


output = bind_rows(output) %>% 
  unnest(x) %>% 
  nest(x)

# output %>% 
#   unnest() %>% 
#   unnest(x)
```

```{r}
goutput = output %>% 
  filter(n1_response > 5,
         n1_response + n2_response > 23)
```


```{r}
prior = function(df = output, null = 0.25, stage1n = 20, stage2n = 71, n1 = 6, n2 = 24) {
  res = df %>% 
    unnest(data) %>% 
    mutate(pE1 = dbeta(null, n1_response/stage1n, (stage1n-n1_response)/stage1n),
           pE2 = dbeta(null, (n1_response+n2_response)/stage2n, (stage2n-n1_response-n2_response)/stage2n),
           pE = pE1 * pE2,
           pS = dbeta(null+x, 25, 75)) %>% 
    filter(n1_response > n1-1,
           n1_response + n2_response > n2-1)
  
  res  = res %>% 
    filter(pE>pS) %>% 
    group_by(x) %>% 
    mutate(alpha = 1 - length(x)/nrow(goutput)) %>% 
    select(x, alpha) %>% 
    distinct() %>% 
    filter(alpha < .2)
  return(res)
}
res = prior()
```



```{r}
delta_finder = function(df = map_df4, null = 0.25) {
  df %>% 
    mutate(pS = dbeta(null+x, 25, 75))
}
```

```{r}
map_df4 = delta_finder()
```

```{r}
head(map_df4)

head(map_df4) %>% 
  unnest()
```

```{r}
map_filt = function() {
  unnest() %>% 
    filter((n1_response + n2_response) > n2-1,
         (n1_response + n2_response + n3_response) > n3-1)
}
```

```{r}
map_df4 = map_df4 %>% 
  mutate(data = map(data, ~map_filt))
```

```{r ev8}
map_df4 = map_df4 %>% 
  unnest() %>%
  filter((n1_response + n2_response) > n2-1,
         (n1_response + n2_response + n3_response) > n3-1) %>% 
  group_by(x) %>% 
  mutate(nm = n()) %>% 
  ungroup() %>%
  filter(pE1>pS,
         pE2>pS,
         pE3>pS,
         pE4>pS) %>% 
  group_by(x) %>%
  summarize(nm = nm,
            n = n(),
            alpha = 1 - n/nm) %>%
  filter(alpha < 0.3) %>%
  distinct()
```

```{r}
map_df4

map_df4 %>% 
  unnest() %>% 
  arrange(desc(alpha))
```


```{r, eval = FALSE}
fill4 = function(df = map_df4) {
  fin_df = df %>% 
    unnest() %>% 
    group_by(x) %>% 
    mutate(nm = n()) %>% 
    ungroup() %>%
    filter(pE1>pS,
           pE2>pS,
           pE3>pS,
           pE4>pS) %>% 
    group_by(x) %>%
    summarize(nm = nm,
              n = n(),
              alpha = 1 - n/nm) %>%
    filter(alpha < 0.3) %>%
    distinct()
  return(fin_df)
}
```


```{r, eval = FALSE}
map_df4 = map_df4 %>%
  mutate(data = map(data, fill4))
```

```{r, eval = FALSE}
map_df4 %>% 
  unnest() %>% 
  arrange(alpha)
```



```{r, echo = FALSE}
output2 = vector(mode = "list", length = 400)
for (i in 1:20) {
  for (j in 1:20) {
    output2[[c(i, j)]] = bind_cols("n1_response" = i, "n2_response" = j)
    output2[[c(i, j)]]$x = list(seq(from = 0.01, to = 0.4, by = 0.003))
  }
  output2[[i]] = map(output2[[i]], ~bind_rows(.))
}


df2 = bind_rows(output2) %>% 
  unnest(x) %>% 
  mutate(id = row_number()) %>% 
  nest(c(n1_response:x))
df2
```

```{r, echo = FALSE}
prior2 = function(df, null = 0.25, stage1n = 20, stage2n = 40, n1 = 6, n2 = 12) {
  res = df %>% 
    # unnest(data) %>% 
    mutate(pE1 = dbeta(null, (0.5+n1_response/stage1n), (1.5+stage1n-n1_response)/stage1n),
           pE2 = dbeta(null, (0.5+n1_response+n2_response)/stage2n, (1.5+stage2n-n1_response-n2_response)/stage2n),
           pS = dbeta(null+x, 25, 75)) %>% 
    filter(n1_response > n1-1,
           (n1_response + n2_response) > n2-1)
  # res = bind_rows(res) %>%
  #   filter(pE1 > pS,
  #          pE2 > pS) %>%
  #   group_by(x) %>%
  #   summarize(x = x,
  #             alpha = length(x)/n())
  #   filter(alpha < .2)
  return(res)
}
```

```{r}
# prior2(df2$data[[1021]])

```



```{r mapdf2, echo = FALSE, eval = FALSE, cache = TRUE}
map_df2 = df2 %>% 
  mutate(data2 = map(data, prior2))
```


```{r, eval = FALSE,cache = TRUE}
map_df2 %>% 
  unnest(data2) %>%
  # group_by(x) %>%
  # summarize(n = n(),
  #           alpha = sum(pE1 > pS & pE2 > pS & n1_response > 5 & (n1_response + n2_response) > 11)) %>% 
  # group_by(x) %>% 
  # summarize(alpha = 1-alpha/n)
  filter(n1_response > 5,
         (n1_response + n2_response) > 11,
         pE1 > pS,
         pE2 > pS) %>%
  group_by(x) %>%
  summarize(n = n(),
            alpha = 1 - n/285) %>%
            # alpha = 1 - n/nrow(df2)) %>%
  filter(alpha < 0.21) %>%
  distinct()
```

```{r, echo = FALSE}
output3 = vector(mode = "list", length = 8000)
for (i in 1:20) {
  for (j in 1:20) {
    output3[[c(i, j)]] = bind_cols("n1_response" = i, "n2_response" = j)
    output3[[c(i, j)]]$k = list(seq(from = 1, to = 20))
    output3[[c(i, j)]]$x = list(seq(from = .1, to = 0.199, by = 0.003))
  }
  output3[[i]] = map(output3[[i]], ~bind_rows(.))
}

df3 = bind_rows(output3) %>% 
  rename("n3_response" = k) %>% 
  unnest(n3_response) %>% 
  unnest(x) %>% 
  mutate(id = row_number()) %>% 
  nest(n1_response:x)
```


```{r, echo = FALSE}
prior3 = function(df = df3, null = 0.25, stage1n = 20, stage2n = 40, stage3n = 60, n1 = 6, n2 = 12, n3 = 18) {
  res2 = df %>% 
    # unnest(data) %>% 
    mutate(pE1 = dbeta(null, (0.5+n1_response)/stage1n, (1.5+stage1n-n1_response)/stage1n),
           pE2 = dbeta(null, (0.5+n1_response+n2_response)/stage2n, (1.5+stage2n-n1_response-n2_response)/stage2n),
           pE3 = dbeta(null, (0.5+n1_response + n2_response + n3_response)/stage3n, (1.5+stage3n-n1_response-n2_response-n3_response)/stage3n),
           pS = dbeta(null+x, 25, 75))
    # filter(n1_response > n1-1,
    #        (n1_response + n2_response) > n2-1,
    #        (n1_response + n2_response + n3_response) > n3-1)
  # res = res %>%
  #   filter(pE3 > pS) %>%
  #   group_by(x) %>%
  #   mutate(alpha = 1 - length(x)/nrow(goutput3)) %>%
  #   select(x, alpha) %>%
  #   distinct() %>%
  #   filter(alpha < .2)
  return(res2)
}
```

```{r mapdf3, echo = FALSE, eval = FALSE, cache = TRUE}
map_df3 = df3 %>% 
  mutate(data3 = map(data, prior3))
```

```{r, eval = FALSE, echo = FALSE}
map_df3 %>% 
  unnest(data3) %>%
  # group_by(x) %>% 
  # summarize(n = n())
  filter(pE1 > pS,
         pE2 > pS,
         pE3 > pS) %>%
  group_by(x) %>%
  summarize(n = n(),
            alpha = 1 - n/5590) %>%
            # alpha = 1 - n/nrow(df2)) %>%
  filter(alpha < 0.21) %>%
  distinct()
```

```{r ev2, eval = FALSE}
output4 = vector(mode = "list", length = 20)
for (i in 1:20) {
  for(j in 1:20) {
    output4[[c(i, j)]] = bind_cols("n1_response" = i, "n2_response" = j)
    output4[[c(i, j)]]$k = list(seq(from = 1, to = 20))
    output4[[c(i, j)]]$l = list(seq(from = 1, to = 11))
    output4[[c(i, j)]]$x = list(seq(from = .15, to = 0.3, by = 0.003))
    output4[[c(i, j)]]$n1 = 7
    output4[[c(i, j)]]$n2 = list(seq(13, 14))
    output4[[c(i, j)]]$n3 = list(seq(19, 21))
    output4[[c(i, j)]]$n4 = 24
  }
  output4[[i]] = map(output4[[i]], ~bind_rows(.))
}
```


```{r ev1, eval = FALSE}
df4 = bind_rows(output4) %>% 
  rename("n3_response" = k,
         "n4_response" = l) %>%
  unnest(n2) %>%
  unnest(n3) %>%
  mutate(id = paste0(n2, ",", n3)) %>%
  unnest(x) %>% 
  unnest(n3_response) %>% 
  unnest(n4_response) %>% 
  nest(-id)
```

```{r}
df4_maker = function(n1 = 7) {
  output4 = vector(mode = "list", length = 20)
  for (i in 1:20) {
    for(j in 1:20) {
      output4[[c(i, j)]] = bind_cols("n1_response" = i, "n2_response" = j)
      output4[[c(i, j)]]$k = list(seq(from = 1, to = 20))
      output4[[c(i, j)]]$l = list(seq(from = 1, to = 11))
      output4[[c(i, j)]]$x = list(seq(from = .15, to = 0.35, by = 0.02))
      output4[[c(i, j)]]$n1 = n1
      # output4[[c(i, j)]]$n2 = list(seq(13, 14))
      # output4[[c(i, j)]]$n3 = list(seq(19, 21))
      output4[[c(i, j)]]$n4 = 24
    }
    output4[[i]] = map(output4[[i]], ~bind_rows(.))
  }
  df4 = bind_rows(output4) %>% 
    rename("n3_response" = k,
           "n4_response" = l) %>%
    unnest(x) %>% 
    unnest(n3_response) %>% 
    unnest(n4_response) %>% 
    nest(-x)
  return(df4)
}
```

By creating a dataframe of all possible outcomes it is possible to calculate the probability of each response rate for each interim analysis. This function creates the responses, there are 20 possible response rates in the first trial, 20 potential response rates in the 2nd trial, 20 potential response rates in the 3rd trial and 11 in the 4th and final trial. This means there are 20x20x20x11 potential outcomes, or 88,000.

```{r}
df5 = df4_maker()
```

```{r}
df5 = df5 %>% 
  mutate(n3 = list(19:21),
         n2 = list(13:14)) %>% 
  unnest(n2) %>% 
  unnest(n3)

# df4
```

I hypothesized that the cutoff rates for futility could be 6 or 7 in each interim analysis to reduce the number of potential futility response rates. With a futility response of 7 in the first trial, there can be a cutoff of 13 (7 + 6) or 14 (7 + 7) in the 2nd round. In the 3rd round there should be between 19 (7 + 6 + 6) and 21 ( 7 + 7 + 7) responses to avoid futility. There must be 24 responses ($S_{71} = 24$) to avoid futility in the final check.

```{r}
prior5 = function(df = df5, null = 0.25, stage1n = 20, stage2n = 40, stage3n = 60, stage4n = 71) {
  # res = vector(mode = "list", length = 2)
  # for (i in 1:2) {
  res5 = df %>% 
    mutate(pE1 = pbeta(null, (0.5+n1_response), (1.5+stage1n-n1_response)),
           pE2 = pbeta(null, (0.5+n1_response+n2_response), (1.5+stage2n-n1_response-n2_response)),
           pE3 = pbeta(null, (0.5+n1_response + n2_response + n3_response), (1.5+stage3n-n1_response-n2_response-n3_response)),
           pE4 = pbeta(null, (0.5+n1_response + n2_response + n3_response + n4_response), (1.5+stage4n-n1_response-n2_response-n3_response-n4_response))) %>% 
           # pS = dbeta(null+pull(df, x), 25, 75))
    filter(n1_response > n1-1,
           # (n1_response + n2_response) > n2-1,
           # (n1_response + n2_response + n3_response) > n3-1,
           (n1_response + n2_response + n3_response + n4_response) > n4-1)
  return(res5)
}
```

I calculated the probability distribution of each response using an updated beta distribution for that number of responses in each trial. Then, I filtered on only the response rates that would pass the futility interim analysis.

```{r}
map_df5 = df5 %>% 
  mutate(data = map(data, prior5))
```

```{r}
map_df51 = map_df5 %>% 
  unnest() %>%
  mutate(pS = qbeta(.25, shape1 = 25, shape2 = 75) + x) %>% 
  filter((n1_response + n2_response) > n2-1,
         (n1_response + n2_response + n3_response) > n3-1)

tail(map_df51, n = 1000L)
```

Then I added the posterior distribution, pS (given), to the dataframe and included the different possible cutoff values of n2 and n3. So, if the probability of choosing the value in the prior based on the updated prior distribution (pE) is greater than the probability of choosing the same value under the posterior (pS) with a buffer of $\delta$ in less than $\alpha$ proportion of cases then the conditions are satisfied.

```{r}
# nmx1 = map_df51 %>% 
#   group_by(x, n2, n3) %>%
#   summarize(nm = n()) 
dist5 = map_df51 %>% 
  # left_join(nmx1, by = c("x", "n2", "n3"), copy = TRUE) %>% 
  # filter(pE1>pS,
  #        pE2>pS,
  #        pE3>pS,
  #        pE4>pS) %>%
  group_by(x, n1_response, n2_response, n3_response, n4_response) %>%
  summarize(n = n(),
            alpha1 = sum(pE1 > pS)/n,
            alpha2 = sum(pE2 > pS)/n,
            alpha3 = sum(pE3 > pS)/n,
            alpha4 = sum(pE4 > pS)/n)
  # filter(alpha1 < 0.5,
  #        alpha2 < 0.5,
  #        alpha3 < 0.5,
  #        alpha4 < 0.5) %>% 
gg5 = dist5 %>% 
  ggplot(aes(x = x)) +
  geom_line(aes(y = alpha1), color = "red") + 
  geom_line(aes(y = alpha2), color = "orange") +
  geom_line(aes(y = alpha3), color = "yellow") +
  geom_line(aes(y = alpha4), color = "green") +
  facet_grid(n2~n3)
```

```{r}
map_df51 %>% 
  filter(abs(pE1 - pE4) < 10e-4,
         abs(pE1 - pE2) < 10e-3,
         abs(pE1 - pE3) < 10e-3)

```


```{r, eval = FALSE}
dist5

gg5
  # arrange(desc(alpha1))
```

# n1 = 6

```{r}
df4 = df4_maker(n1 = 6)

df4 = df4 %>% 
  mutate(n2 = list(12:13),
         n3 = list(18:20)) %>% 
  unnest(n2) %>% 
  unnest(n3)
```

```{r}
df4
```

```{r ev10}
prior4 = function(df= df4, null = 0.25, stage1n = 20, stage2n = 40, stage3n = 60, stage4n = 71) {
  # res = vector(mode = "list", length = 2)
  # for (i in 1:2) {
  res4 = df %>%
    group_by(n1_response, n2_response, n3_response, n4_response) %>% 
    mutate(pE1 = qbeta(null, (0.5+n1_response), (1.5+stage1n-n1_response)),
           pE2 = qbeta(null, (0.5+n1_response+n2_response), (1.5+stage2n-n1_response-n2_response)),
           pE3 = qbeta(null, (0.5+n1_response + n2_response + n3_response), (1.5+stage3n-n1_response-n2_response-n3_response)),
           pE4 = qbeta(null, (0.5+n1_response + n2_response + n3_response + n4_response), (1.5+stage4n-n1_response-n2_response-n3_response-n4_response))) %>% 
           # pS = dbeta(null+pull(df, x), 25, 75))
    filter(n1_response > n1-1,
           # (n1_response + n2_response) > n2-1,
           # (n1_response + n2_response + n3_response) > n3-1,
           (n1_response + n2_response + n3_response + n4_response) > n4-1)
  return(res4)
}
```

```{r}
map_df4 = df4 %>% 
  mutate(data = map(data, prior4))
```

```{r}
dist4 = map_df4 %>% 
  unnest() %>%
  mutate(pS = qbeta(.25, shape1 = 25, shape2 = 75) + x) %>% 
  filter((n1_response + n2_response) > n2-1,
         (n1_response + n2_response + n3_response) > n3-1) %>% 
  group_by(x, n2, n3) %>% 
  summarize(n = n(),
            alpha1 = sum(pE1 > pS)/n,
            alpha2 = sum(pE2 > pS)/n,
            alpha3 = sum(pE3 > pS)/n,
            alpha4 = sum(pE4 > pS)/n)
  # group_by(n2, n3) %>% 
  # nest()
```

```{r}
gg4 = dist4 %>% 
#   group_by(x) %>% 
# # filter(pE1>pS,
# #        pE2>pS,
# #        pE3>pS,
# #        pE4>pS) %>%
  # summarize(n = n(),
  #           alpha1 = 1 - sum(pE1 > pS)/n,
  #           alpha2 = 1 - sum(pE2 > pS)/n,
  #           alpha3 = 1 - sum(pE3 > pS)/n,
  #           alpha4 = 1 - sum(pE4 > pS)/n) %>%
  # filter(alpha1 < 0.2,
  #        alpha2 < 0.2,
  #        alpha3 < 0.2,
  #        alpha4 < 0.2) %>%
  ggplot(aes(x = x)) +
  geom_line(aes(y = alpha1), color = "red") + 
  geom_line(aes(y = alpha2), color = "orange") +
  geom_line(aes(y = alpha3), color = "yellow") +
  geom_line(aes(y = alpha4), color = "green") +
  facet_grid(n2~n3)
```

```{r}
head(map_df4) %>% 
  unnest()

dist4 %>% 
  filter(alpha4 > alpha1)

rbeta(10, 6.5, 14.5)
qbeta(.25, 5.5, 14.5)
qbeta(.25, 25, 75)

gg4
```



```{r, eval = FALSE, echo = FALSE}
# # nmx = map_df4 %>%
# #   group_by(x) %>%
#   summarize(nm = n())
dist4 = function(df = map_df4){
  gg = df %>% 
    group_by(x) %>% 
  # filter(pE1>pS,
  #        pE2>pS,
  #        pE3>pS,
  #        pE4>pS) %>%
    summarize(n = n(),
              alpha1 = 1 - sum(pE1 > pS)/n,
              alpha2 = 1 - sum(pE2 > pS)/n,
              alpha3 = 1 - sum(pE3 > pS)/n,
              alpha4 = 1 - sum(pE4 > pS)/n) %>%
    # filter(alpha1 < 0.5,
    #        alpha2 < 0.5,
    #        alpha3 < 0.5,
    #        alpha4 < 0.5) %>%
    ggplot(aes(x = x)) +
    geom_line(aes(y = alpha1), color = "red") + 
    geom_line(aes(y = alpha2), color = "orange") +
    geom_line(aes(y = alpha3), color = "yellow") +
    geom_line(aes(y = alpha4), color = "green")
  return(gg)
}
```

```{r, echo = FALSE, eval = FALSE}
distr = map_df4 %>% 
  mutate(data = map(data, dist4))
```

```{r, echo = FALSE, eval = FALSE}
head(distr)
```


```{r, eval = FALSE}
map_df4 %>%
  unnest() %>% 
  group_by(x, n2, n3) %>% 
  ggplot(aes(x = x)) +
  geom_point(aes(y = pE1))
  # geom_line(aes(y = pS))
  # facet_grid(. ~ n1_response)
```


```{r, eval = FALSE}
map_df4 %>% 
  ggplot(aes(x = x, fill = n2)) +
  geom_violin(aes(y = pE1, fill = n1_response, group = n2_response))
  # facet_grid(n2_response ~ n1_response)
```


```{r, eval = FALSE}
attempt %>% 
  arrange(desc(alpha))
```

```{r, eval = FALSE}
set.seed(719)
n_sim = 10e5
x = 0.27
dat = tibble(means = c(sum(rbeta(n_sim, shape1 = 7.5, shape2 = 14.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 6.5, shape2 = 15.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 13.5, shape2 = 28.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 12.5, shape2 = 29.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 19.5, shape2 = 42.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 18.5, shape2 = 43.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 24.5, shape2 = 48.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim,
                      sum(rbeta(n_sim, shape1 = 23.5, shape2 = 49.5) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x)) / n_sim))
dat
```

```{r}
means = vector(mode = "list", length = 24)
for (i in 1:24) {
  for (j in 1:4) {
    n = c(20, 40, 60, 71)
    means[[c(i, j)]] = sum(rbeta(n_sim, shape1 = .5 + i, shape2 = 1.5 + n[[j]] - i))
  }
}
```



```{r, eval = FALSE}
set.seed(1)
n_sim = 10e4
x = seq(0.1, 0.19, by = 0.01)
outputx = vector(mode = "list", length = 20)
res = vector(mode = "list", length = 20)
for (i in 1:20) {
  for (j in 1:10) {
    outputx[[c(i, j)]] = sum(rbeta(n_sim, shape1 = .5+i, shape2 =1.5+20-i) > (rbeta(n_sim, shape1 = 25, shape2 = 75) + x[[j]])) / n_sim
    res[[c(i, j)]] = bind_cols("alpha" = outputx[[c(i, j)]], "i" = i, "j" = j)
  }
  res[[i]] = map(res[[i]], ~bind_rows(.))
}
# outputx = bind_rows(outputx)
# outputx
res = bind_rows(res)
res
```

```{r}
prior = function(df = output, null = 0.25, stage1n = 20, stage2n = 71, n1 = 6, n2 = 24) {
  res = df %>% 
    unnest(data) %>% 
    mutate(pE1 = dbeta(null, n1_response/stage1n, (stage1n-n1_response)/stage1n),
           pE2 = dbeta(null, (n1_response+n2_response)/stage2n, (stage2n-n1_response-n2_response)/stage2n),
           pS = dbeta(null+x, 25, 75)) %>% 
    filter(n1_response > n1-1,
           n1_response + n2_response > n2-1)
  
  res  = res %>% 
    filter(pE1>pS,
           pE2>pS) %>% 
    group_by(x) %>% 
    mutate(alpha = 1 - length(x)/nrow(goutput)) %>% 
    select(x, alpha) %>% 
    distinct() %>% 
    filter(alpha < .2)
  return(res)
}
res = prior()
```

```{r}
res
```


```{r}
prior6 = function(df = df5, null = 0.25, stage1n = 20, stage2n = 20, stage3n = 20, stage4n = 11) {
  res6 = df %>% 
    mutate(pE1 = qbeta(null, (0.5+n1_response), (1.5+stage1n-n1_response)),
           pE2 = qbeta(null, (0.5+n2_response), (1.5+stage2n-n2_response)),
           pE3 = qbeta(null, (0.5+n3_response), (1.5+stage3n-n3_response)),
           pE4 = qbeta(null, (0.5+n4_response), (1.5+stage4n-n4_response)))
           # pS = dbeta(null+pull(df, x), 25, 75))
    # filter(n1_response > n1-1,
    #        (n1_response + n2_response) > n2-1,
    #        (n1_response + n2_response + n3_response) > n3-1,
    #        (n1_response + n2_response + n3_response + n4_response) > n4-1)
  return(res6)
}
```


```{r}
map_df6 = df5 %>% 
  mutate(data = map(data, prior6))
```

```{r}
map_df6_nested = map_df6 %>% 
  mutate(pS = qbeta(.25, shape1 = 25, shape2 = 75)) %>% 
  unnest() %>% 
  group_by(x, n1_response, n2_response, n3_response, n4_response) %>% 
  mutate(alpha1 = (pE1 > pS + x),
         alpha2 = (pE2 > pS + x),
         alpha3 = (pE3 > pS + x),
         alpha4 = (pE4 > pS + x)) %>% 
  ungroup() %>%
  group_by(n1_response, n2_response, n3_response, n4_response) %>%
  nest()
#   return(res61)
# }
```

```{r}
map_df61_nested = map_df6_nested %>% 
  mutate(data = map(data, ~filter(., alpha1 > 0.2,
                                  alpha2 > 0.2,
                                  alpha3 > 0.2,
                                  alpha4 > 0.2)))
```

```{r}
map_df61_nested %>% 
  unnest() %>% 
  select(x, n1_response, n2_response, n3_response, n4_response, pE1, pE2, pE3, pE4, pS, alpha1, alpha2, alpha3, alpha4) %>% 
  distinct() %>% 
  filter(x == 0.15) %>% 
  head()
```

```{r, eval = FALSE}
# nmx1 = map_df51 %>% 
#   group_by(x, n2, n3) %>%
#   summarize(nm = n()) 
dist5 = map_df51 %>% 
  # left_join(nmx1, by = c("x", "n2", "n3"), copy = TRUE) %>% 
  # filter(pE1>pS,
  #        pE2>pS,
  #        pE3>pS,
  #        pE4>pS) %>%
  group_by(x, n1_response, n2_response, n3_response, n4_response) %>%
  summarize(n = n(),
            alpha1 = sum(pE1 > pS)/n,
            alpha2 = sum(pE2 > pS)/n,
            alpha3 = sum(pE3 > pS)/n,
            alpha4 = sum(pE4 > pS)/n)
  # filter(alpha1 < 0.5,
  #        alpha2 < 0.5,
  #        alpha3 < 0.5,
  #        alpha4 < 0.5) %>%
```


```{r, eval = FALSE}
gg5 = map_df51$data[[7]] %>% 
  ggplot(aes(x = x)) +
  geom_line(aes(y = alpha1), color = "red") + 
  geom_line(aes(y = alpha2), color = "orange") +
  geom_line(aes(y = alpha3), color = "yellow") +
  geom_line(aes(y = alpha4), color = "green") +
  facet_grid(n2~n3)
```

```{r, eval = FALSE}
map_df51 %>% 
  filter(abs(pE1 - pE4) < 10e-4,
         abs(pE1 - pE2) < 10e-3,
         abs(pE1 - pE3) < 10e-3)

```